### 2012-11-25 paper.tex
asdf
removed column 'correctly classified'

\begin{table}[h]
\centering
\begin{tabular}{llllllll}
	\toprule
									&TP Rate   	&FP Rate   &Precision &Recall  &F-Measure   &  Correctly classified\\
	\midrule
	Decision Tree		\\
  Random Forest		\\
  Naive Bayes			&   0.897  & 0.244   & 0.958     & 0.897  & 0.92     \\
  SVM							&0.959     	&0.959     	&0.919   	&0.959   &0.939     	&	0.959\\
  kNN							&0.959     	&0.959     	&0.919   	&0.959   &0.939     	&	0.959\\
	\bottomrule
\end{tabular}
\caption{Comparison of the different algorithms for the echocardiogram dataset}
\end{table}

@@

\begin{table}[h]
\centering
\begin{tabular}{llllllll}
	\toprule
									&TP Rate   	&FP Rate   &Precision &Recall  &F-Measure   &  Correctly classified\\
	\midrule
	Decision Tree		& 0.86    	& 0.307   	& 0.854   & 0.86   & 0.855     & 		& FEHLT\\
  Random Forest		& 0.859   	& 0.333   	& 0.853   & 0.859  & 0.851     	& FEHLT\\
  Naive Bayes		 	&  0.83    & 0.186   & 0.854     & 0.83   & 0.837     \\
  SVM							& 0.849    	& 0.343     &0.842   	&0.849   &0.842     	& 0.849\\
  kNN							&0.835     	&0.331      &0.829    &0.835   &0.831				& 0.835\\
	\bottomrule
\end{tabular}
\caption{Comparison of the different algorithms for the adult dataset}
\end{table}

@@

\begin{table}[htb]
\centering
\begin{tabular}{lllllll}
	\toprule
	&								TP Rate   	&FP Rate   &Precision   &Recall  &F-Measure     	&Class\\ 
	\midrule
									&0.583     	&0.355     &0.55      	&0.583   &0.566   		    	&1\\
                 	&0.393     	&0.181     &0.389     	&0.393   &0.391      	    	&2\\
                 	&0.444     	&0.252     &0.484     	&0.444   &0.463      	    	&3\\
	Weighted Avg.   & 0.849    & 0.343      &0.842   &  0.849     &0.842     			&\\
	\bottomrule
\end{tabular}
\caption{Results of the SVM-classification for the contraception dataset}
\end{table}

@@

\begin{table}[h]
\centering
\begin{tabular}{llllllll}
	\toprule
									&TP Rate   	&FP Rate   &Precision &Recall  &F-Measure   &  Correctly classified\\
	\midrule
	Decision Tree 	&  0.558   & 0.243   & 0.557     	& 0.558  & 0.557     & FEHLT\\
  Random Forest		&  0.556   & 0.241   & 0.562     	& 0.556  & 0.556     & FEHLT\\
  Naive Bayes		 	&  0.508   & 0.243   & 0.528     & 0.508  & 0.513 \\
  SVM							& 0.849    & 0.343   &0.842   		& 0.849  & 0.842 		 & 0.492\\
  kNN							&0.489     &0.284    &0.487     	& 0.489  & 0.488 		 & 0.489\\
	\bottomrule
\end{tabular}
\caption{Comparison of the different algorithms for the contraceptive method choice dataset}
\end{table}
\bibliography{references}

>>>>

\begin{table}[h]
\centering
\begin{tabular}{llllllll}
	\toprule
									&TP Rate   	&FP Rate   &Precision &Recall  &F-Measure \\
	\midrule
	Decision Tree		\\
  Random Forest		\\
  Naive Bayes			&   0.897  & 0.244   & 0.958     & 0.897  & 0.92     \\
  SVM							&0.959     	&0.959     	&0.919   	&0.959   &0.939    \\
  kNN							&0.959     	&0.959     	&0.919   	&0.959   &0.939    \\
	\bottomrule
\end{tabular}
\caption{Comparison of the different algorithms for the echocardiogram dataset}
\end{table}

@@

\begin{table}[h]
\centering
\begin{tabular}{lllllll}
	\toprule
									&TP Rate   	&FP Rate   &Precision &Recall  &F-Measure  \\
	\midrule
	Decision Tree		& 0.86    	& 0.307   	& 0.854   & 0.86   & 0.855     \\
  Random Forest		& 0.859   	& 0.333   	& 0.853   & 0.859  & 0.851    \\
  Naive Bayes		 	&  0.83    & 0.186   & 0.854     & 0.83   & 0.837     \\
  SVM							& 0.849    	& 0.343     &0.842   	&0.849   &0.842     \\
  kNN							&0.835     	&0.331      &0.829    &0.835   &0.831			\\
	\bottomrule
\end{tabular}
\caption{Comparison of the different algorithms for the adult dataset}
\end{table}

@@

\begin{table}[htb]
\centering
\begin{tabular}{lllllll}
	\toprule
	&								TP Rate   	&FP Rate   &Precision   &Recall  &F-Measure     	&Class\\ 
	\midrule
									&0.583     	&0.355     &0.55      	&0.583   &0.566   		    	&1\\
                 	&0.393     	&0.181     &0.389     	&0.393   &0.391      	    	&2\\
                 	&0.444     	&0.252     &0.484     	&0.444   &0.463      	    	&3\\
	Weighted Avg.   &0.492     	&0.28      &0.491     	&0.492   &0.491     			&\\
	\bottomrule
\end{tabular}
\caption{Results of the SVM-classification for the contraception dataset}
\end{table}

@@

\begin{table}[h]
\centering
\begin{tabular}{lllllll}
	\toprule
									&TP Rate   	&FP Rate   &Precision &Recall  &F-Measure   \\
	\midrule
	Decision Tree 	&  0.558   & 0.243   & 0.557     	& 0.558  & 0.557     \\
  Random Forest		&  0.556   & 0.241   & 0.562     	& 0.556  & 0.556     \\
  Naive Bayes		 	&  0.508   & 0.243   & 0.528     	& 0.508  & 0.513 \\
  SVM							& 0.492    &0.280     &0.491     	&0.492   & 0.491 		 \\
  kNN							&0.489     &0.284    &0.487     	& 0.489  & 0.488 		 \\
	\bottomrule
\end{tabular}
\caption{Comparison of the different algorithms for the contraceptive method choice dataset}
\end{table}
\bibliography{references}
